# Activity QC



```{r, echo=FALSE}
library(png)
library(grid)

```

```{r, echo=FALSE}
working_dir="/home/labs/davidgo/Collaboration/MPRA_QC_pipeline/activity/output/"
output_dir=sprintf("%s/test_QC",working_dir)
```

## Activity of controls

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "Control_activity_boxplots.png"),native = T)

bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "Control_activity_boxplots.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "archaic_MPRA", "Control_activity_boxplots.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()
```

## RNA/DNA ratio correlation between replicates - subgroup

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)
bad_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```

## RNA vs. DNA scatter plot

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "RNA_DNA_ratio.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "RNA_DNA_ratio.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "RNA_DNA_ratio.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```


## RNA vs. DNA scatter plot - group of interest - Controls

Lorem Ipsum

```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "RNA_DNA_ratio_w_controls_highlighted.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "RNA_DNA_ratio_w_controls_highlighted.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "RNA_DNA_ratio_w_controls_highlighted.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```


## RNA vs. DNA scatter plot - group of interest - Active vs Non-active

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "RNA_DNA_ratio_active_oligos_highlighted.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "RNA_DNA_ratio_active_oligos_highlighted.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "RNA_DNA_ratio_active_oligos_highlighted.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```


## RNA vs. DNA scatter plot - bcs level

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)
bad_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)

# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```

## GC content bias in DNA counts

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L4a1", "GC_content_bias_in_DNA.png"),native = T)
bad_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "GC_content_bias_in_DNA.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```

## RNA/DNA ratio correlation between replicates

Lorem Ipsum



```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "RNA_DNA_ratio_correlation_between_replicates.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "RNA_DNA_ratio_correlation_between_replicates.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "RNA_DNA_ratio_correlation_between_replicates.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```



## RNA/DNA ratio correlation between replicates - ctrls

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "RNA_DNA_ratio_correlation_between_replicates_with_controls.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "RNA_DNA_ratio_correlation_between_replicates_with_controls.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "RNA_DNA_ratio_correlation_between_replicates_with_controls.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```

## RNA/DNA ratio correlation between replicates - active vs not active

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "RNA_DNA_ratio_correlation_between_replicates_with_highlighted_oligos.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "RNA_DNA_ratio_correlation_between_replicates_with_highlighted_oligos.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "RNA_DNA_ratio_correlation_between_replicates_with_highlighted_oligos.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```

## RNA/DNA ratio correlation between replicates - subgroup

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)
bad_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```

## RNA/DNA ratio correlation with previous experiments (same cell type)

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)
bad_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```




## RNA/DNA ratio correlation with previous experiments (allelic pairs)

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)
bad_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```




## RNA/DNA ratio correlation with previous experiments (allelic pairs)

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "allelic_pairs_correlation.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "allelic_pairs_correlation.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "allelic_pairs_correlation.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```




## RNA/DNA ratio correlation between cell types (Ryder’s graph)Carly’s data

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)
bad_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```




## Activity statistic vs. RNA/DNA

Lorem Ipsum

```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "activity_statistic_vs_RNA_DNA_ratio.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "activity_statistic_vs_RNA_DNA_ratio.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "activity_statistic_vs_RNA_DNA_ratio.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```




## How to measure the droplet shape?

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)
bad_example <- readPNG(file.path(working_dir,"placeholder.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```



## Increasing min(DNA) threshold to decrease noise

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "min_DNA_threshold_noise_analysis.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 1)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(example, interpolate = FALSE)
popViewport()

```



## UMI complexity


Lorem Ipsum

```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "UMI_complexity_histogram.png"),native = T)
bad_example <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "UMI_complexity_histogram.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()


```


## Activity histogram

Lorem Ipsum

```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "power_analysis_activity_histogram.png"),native = T)
bad_example_1 <- readPNG(file.path(working_dir, "humanMPRA_L1a1", "power_analysis_activity_histogram.png"),native = T)
bad_example_2 <- readPNG(file.path(working_dir, "humanMPRA_L1a1_Neurons", "power_analysis_activity_histogram.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 3)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example_1, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 3))
grid.raster(bad_example_2, interpolate = FALSE)
popViewport()

```




## Cumulative RNA reads

Lorem Ipsum


```{r,echo=FALSE}

grid.newpage()

good_example <- readPNG(file.path(working_dir, "humanMPRA_L3a2", "Cumulative RNA reads.png"),native = T)
bad_example <- readPNG(file.path(working_dir, "methMPRA", "Cumulative RNA reads.png"),native = T)


# Start new page and define layout
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))

# Helper to specify location in layout
vplayout <- function(row, col) viewport(layout.pos.row = row, layout.pos.col = col)

# Draw both images in the layout without using print()
pushViewport(vplayout(1, 1))
grid.raster(good_example, interpolate = FALSE)
popViewport()

pushViewport(vplayout(1, 2))
grid.raster(bad_example, interpolate = FALSE)
popViewport()

```















